The Geometry of Archaeological Thought: Analysing discplinary change using word embeddings from conference abstracts

### 2020-05-28 documents/paper.Rmd
update method section

LW: We generated the word embeddings on the co-occurrence matrix using the GloVe algorithm from the text2vec package for R [@Pennington2014; @Selivanov2016]. GloVe (Global Vectors) is a unsupervised learning model that creates word vectors to represent semantic regularity and capture relationships between words [@Pennington2014; @Garg2018].

>>>>

LW: We generated the word embeddings on the co-occurrence matrix using the GloVe algorithm from the text2vec package for R [@Pennington2014; @Selivanov2016]. GloVe (Global Vectors) is an unsupervised learning model that creates word vectors to represent semantic regularity and capture relationships between words [@Pennington2014; @Garg2018]. The general idea underlying the model is that the multiplied value of word vectors i and j will meet the logarithm of the co-occurrence count of word i and j in the matrix. Following this principle, GloVe performs a logistic regression continuously for every word along the text to decide vector values by maximizing the probability of a surrounding word with the occurrence of a center word. It involves three steps to complete this task. First, it adds intercepts associated with each word in a pair to compensate for the difference between the average of a word vector and its weighted sum. Second, it minimizes the sum of all squared errors from the previous step by giving weight to vectors with a function. Third, it deals with word pairs with large co-occurrence count to avoid a skewed number. Finally, GloVe generates two sets of word vectors as the roles of words (i.e. as a center or a surrounding word) in each pair can be reversed when GloVe algorithm moving through. The final output of word vectors is the sum of these two sets of values.
